Network Configuration Synthesis with Abstract Topologies

### 2016-11-13 paper/abstraction/paper.tex
reference to mix-mode networks in abstract topology

\para{Abstract topology}
Abstract topologies in \sysname define structural and role-based invariants that describe a collection of concrete networks. These invariants are encoded in the form of a graph homomorphism annotated with logical constraints about node and edge multiplicities.
%
We designed these abstractions to be able to precisely capture many real network topologies, while also being amenable to fault-tolerance analysis and configuration synthesis.

@@

The role-based abstraction therefore overapproximates the connectivity of the underlying concrete graphs. On its own, this abstraction loses a lot of information about the structure of concrete networks, making it difficult to reason precisely about fault-tolerance.
%which would hinder a useful analysis of its fault-tolerance.
For example, with this abstraction any spine router in a concrete network may or may not be connected to any aggregator router.
%
In order to refine the abstraction to capture more precisely the kinds of concrete networks of interest,
we introduce several additional concepts. The first is the idea of a topology hierarchy captured by P and Q, which indicate that nodes in the ToR and aggregator roles are grouped into a number of smaller pods.
The second is a notion of node and edge \emph{multiplicities}. Each edge (and node) is labelled
with a symbolic variable (\EG, $e1, e2, \ldots$) that denotes a constraint on the number of edges (and nodes) that may appear in any given concrete network. Operators can capture concrete network invariants by adding constraints on the symbolic variables using logical formula.

@@

A final type of abstraction is the $\Mincut(1)$ constraint between the spine role S and N[1--2]. The mincut constraint says that any node in the spine role has at least one path to any node in the neighbor N1 (and N2) role. Annotations of this form are often useful for a "one big switch" abstraction \cite{Casado:2010} in which part of a complex network is represented as a single node. For example, to model an ISP backbone network the operator might divide the network into separate geographic regions with two abstract roles per region -- one role for the border routers of the network, and another role for the core of the network. Mincut annotations can be used to describe the degree of fault tolerance both within region cores as well as across regions.

>>>>

\para{Abstract topology}
Abstract topologies in \sysname define structural and role-based invariants that compactly describe all concrete networks that can emerge as the network evolves. They are encoded in the form of a graph homomorphism annotated with logical constraints about node and edge multiplicities.
%
We designed the abstractions to be able to precisely capture real network topologies, while being amenable to fault-tolerance analysis in the abstract domain.

@@

The role-based abstraction therefore overapproximates the connectivity of the underlying concrete graphs. On its own, this abstraction loses a lot of information about the structure of concrete networks, making it difficult to reason precisely about fault-tolerance.
%which would hinder a useful analysis of its fault-tolerance.
For example, with this abstraction any spine router in a concrete network may or may not be connected to any aggregator router.
%
To capture more precisely the kinds of concrete networks of interest,
we introduce several additional concepts. The first is the idea of a topology hierarchy captured by P and Q, which indicate that nodes in the ToR and aggregator roles are grouped into a number of smaller pods.
The second is a notion of node and edge \emph{multiplicities}. Each edge (and node) is labelled
with a symbolic variable (\EG, $e1$) that denotes a constraint on the number of edges (and nodes) that may appear in any valid concrete network. Operators can capture concrete network invariants by adding constraints on the symbolic variables using logical formulas.

@@

A final type of abstraction is the $\Mincut(1)$ constraint between the spine role S and N[1--2]. It says that any node in the spine role has at least one path to any node in the neighbor N1 (and N2) role. Such annotations are useful for a "one big switch" abstraction \cite{Casado:2010} in which part of a complex network is represented as a single node. For example, to model an ISP backbone network the operator might divide the network into separate geographic regions with two roles per region---one for the border routers and another for the core of the network. Mincut annotations can be used to describe the degree of fault tolerance both within region cores as well as across regions.

Our topology abstractions can trivially capture concrete topologies; there will be a one-to-one correspondence between abstract and concrete nodes (and edges). This ability enables operators to define complex networks in which they expect some (e.g., legacy) parts of the network to not evolve and others to evolve. It also means that our compiler subsumes those that operate only over concrete topologies.
